Article Title

### 2014-01-24 plos.tex
Rev 41. Incorporated Andreas' comments.

\section*{Abstract}
% Please keep the abstract between 250 and 300 words
Ambitious projects aim to record the activity of ever larger and denser neuronal populations \emph{in vivo}.  Correlations in neural activity measured in such recordings can reveal important aspects of the organization of neural circuits.  However, estimating and interpreting large correlation matrices is challenging.  Estimation can be improved by regularization, \ie by imposing a structure on the estimate.  The amount of improvement depends on how closely the assumed structure represents dependencies in the data. Therefore, the selection of the most efficient correlation matrix estimator for a given neural circuit must be determined empirically.  Importantly, the identity and structure of the most efficient estimator informs about the types of dominant dependencies governing the system.

@@

It is now possible to record the spiking activity of hundreds of neurons at the same time.  A meaningful statistical description of the collective activity of these neural populations -- their \sq{functional connectivity} -- is a forefront challenge in neuroscience.  We addressed this problem by identifying statistically efficient estimators of correlation matrices of the spiking activity of neural populations.  Various underlying processes may reflect differently on the structure of the correlation matrix:  Correlations due to common network fluctuations or external inputs are well estimated by low-rank representations, whereas correlations due to linear interactions between specific pairs of neurons are well approximated by their pairwise \emph{partial} correlations.  In our data obtained from fast 3D two-photon imaging of calcium signals of large and dense groups of neurons in mouse visual cortex, the best estimation performance was attained by decomposing the correlation matrix into a sparse network of partial correlations (\sq{interactions}) combined with a low-rank component. The inferred interactions were both positive (\sq{excitatory}) and negative (\sq{inhibitory}) and reflected the spatial organization and orientation preferences of the interacting cells.  We propose that the composition of the most efficient among many estimators provides a more informative picture of the functional connectivity than previous analyses of neural correlations.
\section*{Introduction}
\emph{Functional connectivity} is a statistical description of \emph{multineuronal} activity patterns not reducible to the response properties of the individual cells.  Functional connectivity is expressed as the degree of correlation, synchronization, or other forms of statistical association between neurons, or in the form of multineuronal coactivation patterns, or by fitting a probabilistic model of the population activity.  Functional connectivity is thought to reflect local synaptic connections, shared inputs from other regions, and endogenous network activity.  Although functional connectivity is only a phenomenological description with no simple mechanistic interpretation, it can be used to generate or test hypotheses about the anatomical architecture of the neural circuit and the processing of information at the population level.

@@

Neural correlations do not come with ready or unambiguous mechanistic interpretations. They can arise from monosynaptic or polysynaptic interactions, common or correlated inputs, oscillations, top-down modulation, and background network fluctuations \cite{Perkel:1967, Moore:1970, Shadlen:1998, Salinas:2001, Ostojic:2009, Rosenbaum:2011}. But multineuronal recordings do provide more information than available from an equivalent number of pairs of cells considered separately. For example, the eigenvalue decomposition of the covariance matrix expresses shared correlated activity components across the population; common fluctuations of population activity may be accurately represented by just a few principal components but will affect all correlation coefficients. On the other hand, a correlation matrix can be specified through the  partial correlations between pairs of the recorded neurons. The partial correlation coefficient between two neurons reflects their linear association conditioned on the activity of all the other recorded cells.  For this reason, partial correlations have been proposed to more closely reflect the direct causal effects between components of complex systems than correlations; partial correlations have been used to describe interactions between genes in functional genomics \cite{Schafer:2005, Peng:2009} and between brain regions in imaging studies \cite{Varoquaux:2012, Ryali:2012}.

However, estimation of covariance matrices from large populations presents a number of numerical challenges. The amount of recorded data grows only linearly with population size whereas the number of estimated coefficients increases quadratically. This mismatch leads to an increase in spurious correlations, overestimation of common activity (\ie overestimation of large eigenvalues) \cite{Ledoit:2004}, and poorly conditioned partial correlations \cite{Schafer:2005}. All prior empirical findings from neural correlations have used \emph{sample correlations}.  The \emph{sample correlation matrix} is an unbiased estimate but its many free parameters make it sensitive to the sampling noise. As a result, on average, the sample correlation matrix is farther from the true correlation matrix than some structured estimates.

@@

Reduced estimation error is not the only benefit of regularization.  By finding the most efficient estimator for a specific system among many regularized estimators, we learn something about the system itself: Since imposing this structure leads best estimation, the elements of the structure may provide a better representation of the underlying dependencies in the data than previous analyses of sample correlations.

@@

To address these questions, we evaluated four regularized covariance matrix estimators that imposed different structures on the estimate. The estimators are designated as follows:
\begin{description}
\item[$C_{\sf 0}$] -- sample covariance matrix, the unbiased, unregularized estimator.
\item[$C_{\sf diag}$] -- linear shrinkage of correlations toward zero.
\item[$C_{\sf factor}$] -- linear shrinkage of the covariances toward a low-rank matrix, representing inputs from unobserved factors.
\item[$C_{\sf sparse}$] -- sparse partial correlations, \ie a large fraction of the \emph{partial} correlations between pairs of neurons are set to zero.
\item[$C_{\sf sparse+latent}$] -- sparse partial correlations between the recorded neurons \emph{and} linear interactions with a number of latent units.
\end{description}

@@

We therefore performed a cross-validated evaluation to establish which of the four regularized estimators was most efficient for the population activity of dense groups of neurons in mouse primary visual cortex recorded with high-speed 3D random-access two-photon imaging of calcium signals. We found that $C_{\sf sparse+latent}$ consistently outperformed the other estimators.  This estimator revealed a sparse network of partial correlations between the observed neurons and inferred several latent units exerting linear effects on the observed neurons. We analyzed these networks of partial correlations and found the following: Whereas noise correlations were predominantly positive, the inferred partial correlations had a large fraction of negative values possibly reflecting inhibitory circuitry.  Moreover, we found that the inferred positive partial correlations exhibited stronger dependencies with respect to physical distances and differences in preferred orientations than noise correlations. In contrast, the inferred negative partial correlations were less selective.

\section*{Results}
% Results and Discussion can be combined.
\paragraph{Covariance estimation}
The covariance matrix is defined as
\begin{equation}\label{eq:true-covariance}
    \Sigma = \E{(x-\mu)(x-\mu)^\T},\quad \mu = \E{x}
\end{equation}
where $\E{\cdot}$ denotes expectation; the $p\times 1$ vector $x$ is a single observation the firing rates of $p$ neurons over time $\Delta t$; and $\mu$ is the vector of expected firing rates.  The usual way to estimate the covariance matrix is to calculate the \emph{sample covariance matrix} $C_{\sf 0}$ from the empirical sample of observations $x(t),\; t=1,\ldots,n$ as
\begin{equation}
    C_{\sf 0} = \frac 1 \nu \sum\limits_{t=1}^n (x(t)-\bar x)(x(t)-\bar x)^\T,\quad \bar x= \frac 1 n \sum\limits_{t=1}^n x(t)
\end{equation}
where $\nu$ is the number of degrees of freedom in one neuron's activity within the sample ($\nu=n-1$ if observations are independent). For noise correlations, the true mean $\mu$ and the sample mean $\bar x$ are conditioned on the stimulus. In this study, we estimate the true mean, $\mu$, using the sample mean $\bar x$, but seek a better estimate of the covariance matrix than the sample correlation matrix, $C_{\sf 0}$.

@@

We considered four regularized estimators based on distinct families of reduced target estimates: $C_{\sf diag}$, $C_{\sf factor}$, $C_{\sf sparse}$, and $C_{\sf sparse+latent}$. In probabilistic models with exclusively linear dependencies, the targets estimates of these for estimators correspond to distinct families of graphical models (\figref{02}{\,Row 1}}).

@@

The target estimate of estimator $C_{\sf diag}$ is the diagonal matrix $D$ containing estimates of neurons' variances. Regularization is achieved by linear \emph{shrinkage} of the unbiased estimate $C_{\sf 0}$ toward $D$ controlled by the scalar \emph{shrinkage intensity} parameter $\lambda \in [0, 1]$:
\begin{equation}\label{eq:c-diag}
C_{\sf diag} = (1-\lambda) C_{\sf 0} + \lambda D
\end{equation}
The structure of imposed by $C_{\sf diag}$ favors populations with no linear associations between the neurons (\figref{02}{Row 1, A}).  If sample correlations arise from spurious or contingent effects, $C_{\sf diag}$ is expected to be more efficient than other estimators.

@@

\begin{FPfigure}
    \begin{center}
        \includegraphics[width=17.35cm]{./figures/Figure05.pdf}
    \end{center}
    \caption{{\bf Example of low-dimensional correlation structure revealed by the sparse+low-rank estimator.}
    {\bf A.} The regularized estimate of the correlation matrix (top-right) closely approximates the sample correlation matrix (bottom left). 
    This close approximation is  also demonstrated by the scatter plot of the correlation coefficients produced by the two estimates ({\bf D}). 
    However, the partial correlation matrices from the two estimates show more pronounced differences ({\bf B} and {\bf E}). 
    {\bf C.} The partial correlation matrix of the regularized estimate is decomposed into a sparse component with 82.2\% off-diagonal zeros (bottom-left) and low-rank component of rank 15 (top-right).
    {\bf F.} The sparse component of the regularized partial correlation matrix had little resemblance to the sample correlations. The gray interval indicates the range of correlations containing 82.2\% of cells pairs, equal to the fraction of zeros in the sparse partial correlation matrix. This interval contained 58.3\% of the partial correlations. 
    {\bf G.} A graphical depiction of the positive (green) and negative (magenta) partial correlations as edges between observed neurons. The line density is proportional to the magnitude of the correlation.
    {\bf H.} A subset of neurons from the center of the cluster shown in {\bf G} showing the regularized partial correlations.
    {\bf I.} The same subset with sample correlations thresholded to match the sparsity of the regularized interactions.
}
\label{fig:05}
\end{FPfigure}

@@

\begin{figure}[!ht]
    \begin{center}
        \includegraphics{./figures/Figure06.pdf}
    \end{center}
    \caption{{\bf Properties of sparse+low-rank regularized estimates from all imaged sites}
\\
    {\bf A.} The average sample correlations vs.~average partial correlations for each imaged site. In each plot, the red asterisk indicates the site shown in figures \ref{fig:03} and \ref{fig:05}.
    {\bf B.} The average node degree for sparse partial correlations vs.~population size in each imaged site. 
    {\bf C.} The number of inferred latent units vs.~population size in each imaged site.
    {\bf D.} The number latent units vs.~average node degree for sparse partial correlations for each site.
}
\label{fig:06}
\end{figure}

@@

\begin{figure}[!ht]
    \begin{center}
        \includegraphics{./figures/Figure07.pdf}
    \end{center}
    \caption{{\bf Dependence of sample correlations and regularized partial correlations on orientation tuning and physical distance.}
    {\bf A--C.} Average partial correlations (red) estimated by $C_{\sf sparse+latent}$ and average sample correlations (black) averaged across multiple imaged sites. In each site, the correlations were normalized by the respective average correlation shown in Fig.\;\ref{fig:06}\,A.  The number $n$ of sites that qualified to be included in the analysis is indicated. Sites were included if they had at least 20 pairs of neurons in each of the intervals. The error bars indicate the standard error of the mean for based on $n$.
    {\bf A.} Average correlations between pairs of neurons tuned to orientation with differences in preferred orientation in the intervals of 0--15$^\circ$, 15--45$^\circ$ and 45--90$^\circ$. 
    {\bf B.} Average correlations between pairs of neurons located at the same depth ($\pm$25$\mu$m) separated by lateral distances in the intervals of 0--25 $\mu$m, 25--75 $\mu$m, 75--150 $\mu$m, and 150+ $\mu$m.
    {\bf C.} Average correlations between pairs of neurons displaced laterally by less than 25 $\mu$m separated in depth by distances in the intervals of 0-25 $\mu$m, 25--60 $\mu$m, and 60+ $\mu$m.
    {\bf D--F.} Normalized connectivity of positive (green) and negative (dark red) interactions from the sparse component obtained from $C_{\sf sparse+latent}$. Normalized connectivity was computed as the fraction of pairs connected by interactions of corresponding signs in each interval divided by the fraction of non-zero interactions across the entire site. Site were included in the analysis only if they had at least 20 cell pairs in each interval. The error bars indicate the standard error of the mean based on the number $n$ of sites included in the analysis.
}
\label{fig:07}
\end{figure}

@@

Since optimal regularization schemes are specific to systems under investigation, the inference of functional connectivity in big neural data will entail the search for optimal regularizations that may involve combinations of heuristic rules and numerical techniques specifically designed for each type of neural circuit.

@@

The results of model selection must be interpreted with caution.  As we demonstrated by simulation, a simple model can produce a better estimate even if it does not correctly represent the real dependencies in the data than a more complex model with correct representation of dependencies.   Therefore, showing that a more constrained model has better cross-validated performance than a more complex model does not support the inference that it reveals a better representation of dependencies in the data.  This caveat is related to the phenomenon known as \emph{Stein’s Paradox} \cite{Efron:1977}: in which the biasing of an estimate toward an arbitrary target is guaranteed to produce \emph{some} improvement over the best unbiased estimate.

\paragraph{Physiological interpretation and future directions}
Although the network of interactions inferred by the optimal estimator, $C_{\sf sparse+latent}$, resembles a network of synaptic interactions, it is unlikely that the anatomical and functional networks are identical.  The improved estimation performance gives the model extra credence over other estimates of the functional connectivity.  The inferred interaction network was substantially different from that inferred from by considering the network of most significant sample correlations \figref{05}{F, H, and I}.  The $C_{\sf sparse+latent}$ estimator reveals a large number of negative interactions that are not present in the sample correlation matrix (\figref{05}{F}).  These negative interactions are produced as explanations for low sample correlation values where high values are expected based on common correlations with other neurons.  The sample correlation matrix does not draw attention to such surprisingly low correlations and potentially misses their physiological significance.  The resulting network had a larger fraction of negative interactions than in the sample correlation matrix. The negative interactions had a distinct spatial and functional organization from the positive interactions.  To determine potential physiological significance of the negative interactions, future experiments with labeled cell types could indicate whether the negative interactions emanate preferentially from inhibitory cells.

@@

We propose that the structure of the most efficient among many estimators provides a better picture of the functional connectivity than that obtained from unbiased sample correlations.

>>>>

\section*{Abstract}
% Please keep the abstract between 250 and 300 words
Ambitious projects aim to record the activity of ever larger and denser neuronal populations \emph{in vivo}.  Correlations in neural activity measured in such recordings can reveal important aspects of the organization of neural circuits.  However, estimating and interpreting large correlation matrices is statistically challenging.  Estimation can be improved by regularization, \ie by imposing a structure on the estimate.  The amount of improvement depends on how closely the assumed structure represents dependencies in the data. Therefore, the selection of the most efficient correlation matrix estimator for a given neural circuit must be determined empirically.  Importantly, the identity and structure of the most efficient estimator informs about the types of dominant dependencies governing the system.

@@

It is now possible to record the spiking activity of hundreds of neurons at the same time.  A meaningful statistical description of the collective activity of these neural populations -- their \sq{functional connectivity} -- is a forefront challenge in neuroscience.  We addressed this problem by identifying statistically efficient estimators of correlation matrices of the spiking activity of neural populations.  Various underlying processes may reflect differently on the structure of the correlation matrix:  Correlations due to common network fluctuations or external inputs are well estimated by low-rank representations, whereas correlations due to linear interactions between specific pairs of neurons are well approximated by their pairwise \emph{partial} correlations.  In our data obtained from fast 3D two-photon imaging of calcium signals of large and dense groups of neurons in mouse visual cortex, the best estimation performance was attained by decomposing the correlation matrix into a sparse network of partial correlations (\sq{interactions}) combined with a low-rank component. The inferred interactions were both positive (\sq{excitatory}) and negative (\sq{inhibitory}) and reflected the spatial organization and orientation preferences of the interacting cells.  We propose that the composition of the most efficient among many estimators provides a more informative picture of the functional connectivity than previous analyses of neural correlations.

\section*{Introduction}
\emph{Functional connectivity} is a statistical description of observed \emph{multineuronal} activity patterns not reducible to the response properties of the individual cells. Functional connectivity is thought to reflect local synaptic connections, shared inputs from other regions, and endogenous network activity.  Although functional connectivity is only a phenomenological description with no simple mechanistic interpretation, it can be used to generate or test hypotheses about the anatomical architecture of the neural circuit and the processing of information at the population level.

@@

Neural correlations do not come with ready or unambiguous mechanistic interpretations. They can arise from monosynaptic or polysynaptic interactions, common or correlated inputs, oscillations, top-down modulation, and background network fluctuations \cite{Perkel:1967, Moore:1970, Shadlen:1998, Salinas:2001, Ostojic:2009, Rosenbaum:2011}. But multineuronal recordings do provide more information than available from an equivalent number of pairs of cells considered separately. For example, the eigenvalue decomposition of the covariance matrix expresses shared correlated activity components across the population; common fluctuations of population activity may be accurately represented by just a few principal components but will affect all correlation coefficients. On the other hand, a correlation matrix can be specified through the  partial correlations between pairs of the recorded neurons. The partial correlation coefficient between two neurons reflects their linear association conditioned on the activity of all the other recorded cells.  For this reason, partial correlations have been proposed to more closely reflect the direct causal effects between components of complex systems than correlations; partial correlations have been used to describe interactions between genes in functional genomics \cite{Schafer:2005, Peng:2009} and between brain regions in imaging studies \cite{Varoquaux:2012, Ryali:2012}. These opportunities have not yet been explored in neurophysiological studies: most studies have only consider the distribution of pairwise correlations \cite{Zohary:1994, Bair:2001, Smith:2008, Ecker:2010}.

However, estimation of covariance matrices from large populations presents a number of numerical challenges. The amount of recorded data grows only linearly with population size whereas the number of estimated coefficients increases quadratically. This mismatch leads to an increase in spurious correlations, overestimation of common activity (\ie overestimation of large eigenvalues) \cite{Ledoit:2004}, and poorly conditioned partial correlations \cite{Schafer:2005}. The \emph{sample correlation matrix} is an unbiased estimate of the true correlations but its many free parameters make it sensitive to the sampling noise. As a result, on average, the sample correlation matrix is farther from the true correlation matrix than some structured estimates.

@@

Improved estimation of the correlation matrix is beneficial in itself. For example, improved estimates can be used to optimize  decoding of the population activity. But reduced estimation error is not the only benefit of regularization.  The amount of improvement of estimation is greatest when the structure imposed by regularization limits the solution space but still represents the dominant dependencies in the data. Therefore, by finding the most efficient among many regularized estimators, we learn something about the system itself: the imposed structure of the most efficient estimator is a parsimonious representation of the regularities in the data. The elements of this structure likely provide a better representation of the underlying dependencies in the data than previous analyses of sample correlations.

The necessity and benefits of regularization increase with the size of the recorded population. With the advent of the age of big neural data, the search for optimal regularization schemes will become increasingly relevant for all models of functional connectivity. Since optimal regularization schemes are specific to systems under investigation, the inference of functional connectivity in big neural data will entail the search for optimal regularization schemes that may involve combinations of heuristic rules and numerical techniques specially designed for each neural circuit.

@@

To address these questions, we evaluated four regularized covariance matrix estimators that imposed different structures on the estimate. The estimators are designated as follows:
\begin{description}
\item[$C_{\sf 0}$] -- sample covariance matrix, the unbiased, unregularized estimator.
\item[$C_{\sf diag}$] -- linear shrinkage of correlations toward zero.
\item[$C_{\sf factor}$] -- linear shrinkage of the covariances toward a low-rank matrix, representing inputs from unobserved factors (latent units).
\item[$C_{\sf sparse}$] -- sparse partial correlations, \ie a large fraction of the \emph{partial} correlations between pairs of neurons are set to zero.
\item[$C_{\sf sparse+latent}$] -- sparse partial correlations between the recorded neurons \emph{and} linear interactions with a number of latent units.
\end{description}

@@

We then performed a cross-validated evaluation to establish which of the four regularized estimators was most efficient for the population activity of dense groups of neurons in mouse primary visual cortex recorded with high-speed 3D random-access two-photon imaging of calcium signals. In our data, the sample correlation coefficients were largely positive and low.  We found that the best estimate of the correlation matrix was $C_{\sf sparse+latent}$.  This estimator revealed a sparse network of partial correlations between the observed neurons and inferred several latent units exerting linear effects on the observed neurons. We analyzed these networks of partial correlations and found the following: Whereas noise correlations were predominantly positive, the inferred partial correlations had a large fraction of negative values possibly reflecting inhibitory circuitry.  Moreover, we found that the inferred positive partial correlations exhibited stronger dependencies with respect to physical distances and differences in preferred orientations than noise correlations. In contrast, the inferred negative partial correlations were less selective.

\section*{Results}
% Results and Discussion can be combined.
\paragraph{Covariance estimation}
The covariance matrix is defined as
\begin{equation}\label{eq:true-covariance}
    \Sigma = \E{(x-\mu)(x-\mu)^\T},\quad \mu = \E{x}
\end{equation}
where $\E{\cdot}$ denotes expectation; the $p\times 1$ vector $x$ is a single observation of the firing rates of $p$ neurons over time $\Delta t$; and $\mu$ is the vector of expected firing rates.  The usual way to estimate the covariance matrix is to calculate the \emph{sample covariance matrix} $C_{\sf 0}$ from the empirical sample of observations $x(t),\; t=1,\ldots,n$ as
\begin{equation}
    C_{\sf 0} = \frac 1 \nu \sum\limits_{t=1}^n (x(t)-\bar x)(x(t)-\bar x)^\T,\quad \bar x= \frac 1 n \sum\limits_{t=1}^n x(t)
\end{equation}
where $\nu$ is the number of degrees of freedom in one neuron's activity within the sample ($\nu=n-1$ if observations are independent). For noise correlations, the true mean $\mu$ and the sample mean $\bar x$ are conditioned on the stimulus. In this study, we estimate the true mean, $\mu$, using the sample mean $\bar x$, but seek a better estimate of the covariance matrix than the sample correlation matrix, $C_{\sf 0}$.

@@

We considered four regularized estimators based on distinct families of reduced target estimates: $C_{\sf diag}$, $C_{\sf factor}$, $C_{\sf sparse}$, and $C_{\sf sparse+latent}$. In probabilistic models with exclusively linear dependencies, the target estimates of these estimators correspond to distinct families of graphical models (\figref{02}{\,Row 1}}).

@@

The target estimate of estimator $C_{\sf diag}$ is the diagonal matrix $D$ containing estimates of neurons' variances. Regularization is achieved by linear \emph{shrinkage} of the unbiased estimate $C_{\sf 0}$ toward $D$ controlled by the scalar \emph{shrinkage intensity} parameter $\lambda \in [0, 1]$:
\begin{equation}\label{eq:c-diag}
C_{\sf diag} = (1-\lambda) C_{\sf 0} + \lambda D
\end{equation}
The structure imposed by $C_{\sf diag}$ favors populations with no linear associations between the neurons (\figref{02}{Row 1, A}).  If sample correlations arise from spurious effects, $C_{\sf diag}$ is expected to be more efficient than other estimators.

@@

\begin{FPfigure}
    \begin{center}
        \includegraphics[width=17.35cm]{./figures/Figure05.pdf}
    \end{center}
    \caption{{\bf Example of low-dimensional correlation structure revealed by the sparse+latent estimator.}
    {\bf A.} The regularized estimate of the correlation matrix (top-right) closely approximates the sample correlation matrix (bottom left). 
    This close approximation is  also demonstrated by the scatter plot of the correlation coefficients produced by the two estimates ({\bf D}). 
    However, the partial correlation matrices from the two estimates show more pronounced differences ({\bf B} and {\bf E}). 
    {\bf C.} The partial correlation matrix of the regularized estimate is decomposed into a sparse component with 82.2\% off-diagonal zeros (bottom-left) and low-rank component of rank 15 (top-right).
    {\bf F.} The sparse component of the regularized partial correlation matrix had little resemblance to the sample correlations. The gray interval indicates the range of correlations containing 82.2\% of cells pairs, equal to the fraction of zeros in the sparse partial correlation matrix. This interval contained 58.3\% of the partial correlations. 
    {\bf G.} A graphical depiction of the positive (green) and negative (magenta) partial correlations as edges between observed neurons. The line density is proportional to the magnitude of the correlation.
    {\bf H.} A subset of neurons from the center of the cluster shown in {\bf G} showing the regularized partial correlations.
    {\bf I.} The same subset with sample correlations thresholded to match the sparsity of the regularized interactions.
}
\label{fig:05}
\end{FPfigure}

@@

\begin{figure}[!ht]
    \begin{center}
        \includegraphics{./figures/Figure06.pdf}
    \end{center}
    \caption{{\bf Properties of sparse+latent estimates from all imaged sites}
\\
    {\bf A.} The average sample correlations vs.~average partial correlations for each imaged site. In each plot, the red asterisk indicates the site shown in figures \ref{fig:03} and \ref{fig:05}.
    {\bf B.} The average node degree for sparse partial correlations vs.~population size in each imaged site. 
    {\bf C.} The number of inferred latent units vs.~population size in each imaged site.
    {\bf D.} The number latent units vs.~average node degree for sparse partial correlations for each site.
}
\label{fig:06}
\end{figure}

@@

\begin{figure}[!ht]
    \begin{center}
        \includegraphics{./figures/Figure07.pdf}
    \end{center}
    \caption{{\bf Dependence of sample correlations and regularized partial correlations on orientation tuning and physical distance.}
    {\bf A--C.} Average partial correlations (red) estimated by $C_{\sf sparse+latent}$ and average sample correlations (black) averaged across multiple imaged sites. In each site, the correlations were normalized by the respective average correlation shown in Fig.\;\ref{fig:06}\,A.  The number of sites, $n$, that qualified to be included in the analysis is indicated in each panel. Sites were included if they had at least 20 pairs of neurons in each of the intervals. The error bars indicate the standard error of the mean based on on the number of sites $n$.
    {\bf A.} Average correlations between pairs of neurons tuned to orientation with differences in preferred orientation in the intervals of 0--15$^\circ$, 15--45$^\circ$ and 45--90$^\circ$. 
    {\bf B.} Average correlations between pairs of neurons located at the same depth ($\pm$25$\mu$m) separated by lateral distances in the intervals of 0--25 $\mu$m, 25--75 $\mu$m, 75--150 $\mu$m, and 150+ $\mu$m.
    {\bf C.} Average correlations between pairs of neurons displaced laterally by less than 25 $\mu$m separated in depth by distances in the intervals of 0-25 $\mu$m, 25--60 $\mu$m, and 60+ $\mu$m.
    {\bf D--F.} Normalized connectivity of positive (green) and negative (dark red) interactions from the sparse component obtained from $C_{\sf sparse+latent}$. Normalized connectivity was computed as the fraction of pairs connected by interactions of corresponding signs in each interval divided by the fraction of non-zero interactions across the entire site. Site were included in the analysis only if they had at least 20 cell pairs in each interval. The error bars indicate the standard error of the mean based on the number $n$ of sites included in the analysis.
}
\label{fig:07}
\end{figure}

@@

@@

The results of model selection must be interpreted with caution.  As we demonstrated by simulation, a simple model can produce a better estimate even if it does not correctly represent the real dependencies in the data than a more complex model with correct representation of dependencies.   Therefore, showing that a more constrained model has better cross-validated performance than a more complex model does not support the inference that it reveals a better representation of dependencies in the data.  This caveat is related to the phenomenon known as \emph{Stein's Paradox} \cite{Efron:1977}: in which the biasing of an estimate toward an arbitrary target is guaranteed to produce \emph{some} improvement over the best unbiased estimate.

\paragraph{Physiological interpretation and future directions}
Although the network of interactions inferred by the optimal estimator, $C_{\sf sparse+latent}$, resembles a network of synaptic interactions, it is unlikely that the anatomical and functional networks are identical.  The improved estimation performance gives the model extra credence over other estimates of the functional connectivity.  The inferred interaction network was substantially different from that inferred from by considering the network of most significant sample correlations \figref{05}{F, H, and I}.  The $C_{\sf sparse+latent}$ estimator reveals a large number of negative interactions that are not present in the sample correlation matrix (\figref{05}{F}).  These negative interactions are produced as explanations for low sample correlation values where high values are expected based on common correlations with other neurons.  The sample correlation matrix does not draw attention to such surprisingly low correlations and potentially misses their physiological significance.  The resulting network had a larger fraction of negative interactions than in the sample correlation matrix. The negative interactions had a distinct spatial and functional organization from the positive interactions (\figref{fig:07}).  To determine potential physiological significance of the negative interactions, future experiments with labeled cell types could indicate whether the negative interactions emanate preferentially from inhibitory cells.

@@

Here we showed that among several models we tested, we found that for cortical microcircuits, a sparse network of linear interactions with several latent inputs yielded the best estimates of the noise covariance matrix.  This finding valuable in itself: it can be used to improve studies aiming to understand the nature of population coding. Moreover, this estimation approach also provides a graphical representation of the dependencies in the data that can be used to formulate and test hypotheses about the structure of connectivity in the microcircuit.  For example, we find a specific structure of negative interactions which may indicate inhibitory circuitry. Future experiment combining molecular markers for different cell types or follow-up multiple patching in slices \cite{Ko:2012}  with our methods can be used to relate functional connectivity to the circuit architecture. Finally, the graphs of interactions derived \emph{in vivo} could potentially reveal how circuits reconfigure dynamically under different brain states or external stimulation: this opens a window to describe what kinds of interactions are activated by stimulation conditions. Extending the estimation framework to temporal domain is important for future work.

\begin{enumerate}
    \item Better estimator of correlations -- better studies of coding, etc.
    \item The interaction model may give more relevant - validation with new experiments 
    \item Hopefully go beyond static connectivity -- but real-time, emergent, connectivity 
    \item The ideal  experiments  would have causal manipulations 
\end{enumerate}
